\textls[-0]{\thetitle}

### 2023-03-21 casestudies.tex
move a redundant mention of mutually inductive types
composing contradictory features

Composing features can lead to \emph{feature interactions}~\cite{batory2011feature}:
features working correctly in isolation may require coordination when composed.
For example, composing \lsti{STLCIsorec} and \lsti{STLCProd}
(\cref{fig:stlc-isorec-prod}) creates a need to extend \lsti{tysubst} to
handle \lsti{ty_prod}, which the type-checker enforces.

@@

The current plugin implementation does not yet support
mutually inductive types or mutual induction, which are
useful for modeling languages much more complex than STLCs.
However,
we believe accommodating mutually inductive types does
not pose theoretical challenges.

>>>>

Composing features can lead to \emph{feature interactions}~\cite{batory2011feature}:
features working correctly in isolation may require coordination when composed.
For example, composing \lsti{STLCIsorec} and \lsti{STLCProd}
(\cref{fig:stlc-isorec-prod}) creates an obligation to extend \lsti{tysubst} to
handle \lsti{ty_prod}, which the type-checker enforces.
%
Composing contradictory features (e.g., a fixpoints construct and a strong
normalization theorem) would lead to unprovable proof obligations.

@@

%The current plugin implementation does not yet support
%mutually inductive types or mutual induction, which are
%useful for modeling languages much more complex than STLCs.
%However,
%we believe accommodating mutually inductive types does
%not pose theoretical challenges.
